\documentclass[12pt]{article}
\title{AI-powered CYOA dev diary}
\begin{document}



\begin{itemize}
\item[May 13th 2025] Working on the database setup. Realized that
  currently I'm learning how to do the absolute most basic-bitch CRUD
  setup possible, just figuring out how to run Cloud SQL and get a
  local dev environment going for testing, so I should not worry at
  all about database design. For example, can you reuse Locations in
  Stories, or does each Location have a unique Story it's contained
  within? Doesn't matter at all for my purposes today, which are just
  that I can create and read back some dang text from the
  database. So, first milestone: Enable creating new locations,
  listing them, and displaying them on the web UI. They won't have any
  sort of relationships with other objects because today I'm not doing
  DB design, I'm doing DB Hello World.
\item[May 17th] Much struggle setting up protoc and whatnot, since I'm
  not using Bazel any more as I'm used to. Very annoying. Now need to
  figure out how to integrate that in the server.
\item[June 5th] Have completed very basic CRUD setup for
  Locations. Used Jules to produce the boilerplate for the Update and
  Delete operations, not sure it saved me much time but oh well, it
  was an experiment. Next step is to make all this compile on Cloud,
  since I now have two steps, the proto and then the server.
\item[June 13th] Finally completed migration setup for Cloud SQL using
  \verb|migrate.go| script. Gemini was helpful with the basic
  framework but extremely sloppy about getting the strings correct: It
  tried to set me up with a \verb|cloudsqlconn| custom dialer but gave
  me a \verb|unix| DSN. It insisted that the user for IAM
  authentication must be the full email address,
  \verb|runner@whatever.com|, but did not distinguish that from the
  database user for MySQL, which has a length limit of 32 characters
  and was consequently just \verb|runner|. Very much not oneshot
  success here, although on the other hand I'm not sure I would have
  succeeded at all without getting that basic framework, so. Room for
  improvement but still helpful, really.
\item[June 14th] And finally I have it! Refactoring \verb|main.go| to
  use the new initialization was easy enough, but I struggled all day
  with making it authorize correctly to Cloud SQL; it would chuck me
  out every time with ``access denied (using password: YES)''. Well I
  was not using any dang password, and spent literally hours
  confirming that every way I could think of! Finally thought to check
  the CloudSQL-side logs and found that the user was my service runner
  account right enough, but the authentication was still the default
  service account. Apparently gcloud doesn't respect the service
  account set in the trigger! Fixed by adding
\begin{verbatim}
--service-account=cyoa-dev-mysql-runner@${_AR_PROJECT_ID}.iam.gserviceaccount.com
\end{verbatim}
  to the YAML build step. Victory! CRUD now running in the Cloud!
\item[June 16th] So next step is to create Stories, which presumably
  consist of a starting Location and a map from Locations to Actions,
  which may have effects within the Location or may cause a transition
  to a new Location. And having gotten that, I will want to create
  Playthroughs, which reminds me that Stories need to have Characters
  which can be precreated or custom. But first the Actions.
\item[June 25th] I have been plugging away at actions. Copied my
  predicate library out of Landnåm, which saves some work. The Landnåm
  version is on Bazel BUILD files and I cannot be bothered with
  figuring out how to combine that with regular Go build system, so
  copying it is, sigh. Then wrote an E2E test which creates a trivial story,
  two locations and two possible actions in each location, and plays
  through the four possible combinations. When that has four endings
  and passes, well! It'll be frontend time!
\item[June 27th] Ah hah I just realised the problem here. I have a
  backend which handles game mechanics; I want to add a separate,
  pluggable service which adds narrative. So, what if the actions pass
  through the mechanical backend but fail out on the narrative? Could
  in principle gate the transaction commit on it, but seems
  fraught. Think the solution must be: Separate committing ``the
  player did this'' from committing ``these were the effects''. Hum!

  No actually this is not so difficult, just separate out read-only
  loading of state, hypothetical application of action and getting of
  narrative, and actual writing back to DB into separate bits. That
  way you're never left in an inconsistent state.
\item[July 3rd] I've been doing a lot of learning about Vue and have
  finally got my ``Hello Vue'' story editor set up with a full
  database round-trip. This is just a framework, it only edits title
  and description and can't even load a specific story from previous
  sessions, but now that I have the framework and moderately
  understand the build pipeline I can do full-stack work.
\item[July 6th] Some time spent getting the new build steps to work on
  Cloud, and adding a frontpage with a list of stories and
  Create/Edit/Delete links. Today I realized that the story proto
  library, which works excellently for the backend, is not very
  optimal for the transfer between a frontend web app that allows
  editing multiuple locations and actions at the same time, and the
  database that stores them all in separate tables. Spent some time
  thinking about the data model and came up with the StoryContent
  proto which just rolls up a number of Locations and other
  auxilia. That should be relatively easy to translate into JSON and
  Vue.
\item[July 7th] Further data-model work: Migrated to UUIDs for
  locations and actions, which have to be created client-side. Left
  stories and playthroughs, whose creation plausibly involves a server
  roundtrip anyway, as serial integers. I am climbing this here
  learning curve for web apps, yep.
\item[July 12th] Added several editors to the frontend and I think I
  have it, the basic-bitch story editor is ready and I
  proof-of-principled it by creating the ``Defeat the Ogre'' story in
  dev. Next up, playthrough flow including AI narration.
\item[July 17th] Development somewhat slowed as I'm back to work, but
  nonetheless the backend now handles the load-action-return loop
  correctly, including loading new possible actions if the player
  input changes the location. With some minor frontend tweaks it
  should now be possible to run a test game without AI narration.
\item[August 17th] And we have a narration loop with AI! Currently the
  prompt is terrible even for the hello-world escape-the-ogre story,
  but it's proof of principle for the technology. For the record, the
  very first AI-generated narration:
\verbatim{
With a resolute heart, you choose to embody the spirit of a mighty
warrior, a fighter whose strength and courage are renowned across the
lands. Your muscles tense with anticipation as you grip the hilt of
your trusty sword, ready to face any challenge that lies ahead. As you
step into your role, the world around you shifts, and the air grows
thick with the stench of damp earth and danger.

Before you looms a towering ogre, its grotesque form blocking the
path forward. Its eyes gleam with malice, and a low growl rumbles from
its throat as it hefts a massive club. You find yourself at the edge
of a murky swamp, the ground squelching beneath your boots, with
twisted trees casting eerie shadows around you. Your mission is clear:
you must get past this monstrous creature to continue your
journey. The ogre's gaze locks onto you, and it takes a menacing step
forward, daring you to make your move.

You decide to sneak past the ogre, moving with slow, deliberate steps
to avoid drawing its attention. Your heart pounds as you inch along
the shadowed edge of the clearing, barely breathing as the ogre grunts
and shifts its massive bulk. Every rustle of leaves underfoot feels
like a thunderclap, but somehow, the ogre remains oblivious,
distracted by a bone it's gnawing on. After what feels like an
eternity, you manage to slip by unnoticed, though you're still in the
ogre's territory. You must get past the ogre completely to be safe,
and the danger is far from over.
\end{verbatim}
This is dreadful! I chose the suboptimal path of sneaking past the
ogre while playing a fighter, but although the game engine realized I
died as a result, my dev stuff did not get that information into the
prompt and so the poor AI thinks the game continues. That's totally on
me, not the AI, but it also doesn't matter, this is throwaway dev
content that's meant only as a tech proof-of-principle. Also I do need
to figure out how to display the actual text in the webpage, and not
all the metadata like tokens consumed. But all that is just part of
the ordinary development work, the tech-as-such is now in place.
\item[August 30th] Working on templating the AI prompts. Added a debug
  mode that returns the query as the narration. Now also with
  markdown-to-HTML conversion and HTML sanitizing.
\end{itemize}

